---
title: "Targeting Housing Subsidy with People-Based Machine Learning"
author: "Emily Zhou"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: simplex
    toc: yes
    toc_float: yes
    code_folding: hide
    code_download: yes
editor_options:
  markdown:
    wrap: sentence
---

Version 1.0 \| First Created Oct 22, 2023 \| Updated Nov 1, 2023

Keywords: Logistic Regression, Confusion Matrix, ROC Curve, Sensitivity, Specificity, Cost-Benefit Analysis, McFadden R-Squared

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

```{r library and dataset, include=FALSE}
options(scipen=10000000)

library(dplyr)
library(tidyverse)
library(kableExtra)
library(caret)
library(knitr) 
library(pscl)
library(plotROC)
library(pROC)
library(lubridate)
library(patchwork)

palette5 <- c("#DBC2CF","#9FA2B2","#3C7A89","#2E4756","#16262E")
palette4 <- c("#DBC2CF","#9FA2B2","#3C7A89","#2E4756")
palette2 <- c("#DBC2CF","#9FA2B2")
palette1 <- c("#DBC2CF","#16262E")


housing <- read.csv("/Users/emzhou/Desktop/housingSubsidy.csv")
housing <- housing %>% 
  mutate(pdays = as.factor(pdays)) %>% 
  mutate(pdays = ifelse(pdays =="999", "No", "Yes"))
```


# Variables Examination

## Categorical Variables

```{r categorical var, fig.height=10, fig.width=13}

cat_var <- housing %>% 
  select(-c(X, age, y_numeric, previous, unemploy_rate, cons.price.idx, cons.conf.idx, inflation_rate, spent_on_repairs, campaign))
cat_var %>%
    gather(Variable, value, -y) %>%
    count(Variable, value, y) %>%
      ggplot(., aes(value, n, fill = y)) +   
        geom_bar(position = "dodge", stat="identity") +
        facet_wrap(~Variable, scales="free", ncol = 4, 
                   labeller= labeller(Variable = c(
                     `contact` = "Ways of Contact",
                     `day_of_week` = "Day of the Week",
                     `education` = "Educational Attainment",
                     `pdays` = "Days After Contact",
                     `job` = "Occupation Indicator",
                     `marital` = "Marital Status",
                     `month` = "Month of Last Contact",
                     `mortgage` = "Mortgage",
                     `poutcome` = "Previous Campaign Outcome",
                     `taxbill_in_phl` = "Philadelphia Residents",
                     `taxLien` = "Lien"))) +
        scale_fill_manual(values = palette2, name = "Credit") +
        labs(x="Credit", y="Count",
             title = "Feature Associations with the Likelihood of Credit Acceptance",
             subtitle = "Categorical features") +
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(plot.subtitle = element_text(size = 12,face = "italic"),
        plot.title = element_text(size = 18, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
```


```{r chisq test, warning=FALSE}

chi_var <- c("contact", "day_of_week", "education", "job", "marital", "month", "mortgage", "poutcome", "taxbill_in_phl", "taxLien", "pdays")

Label = c("contact" = "Ways of Contact",
          "day_of_week" = "Day of the Week",
          "education" = "Educational Attainment",
          "job" = "Occupation Indicator",
          "marital" = "Marital Status",
          "month" = "Month of Last Contact",
          "mortgage" = "Mortgage",
          "poutcome" = "Previous Campaign Outcome",
          "taxbill_in_phl" = "Philadelphia Residents",
          "taxLien" = "Lien", 
          "pdays" = "Days After Contact")

chi_square_results <- data.frame(
  Df = integer(),
  X_Squared = numeric(),
  P_Value = numeric(),
  stringsAsFactors = FALSE
)

for (var in chi_var) {
  contingency_table <- table(cat_var$y, cat_var[[var]])
  chi_square <- chisq.test(contingency_table)
  chi_square_results <- rbind(chi_square_results, data.frame(
    Df = chi_square$parameter,
    X_Squared = chi_square$statistic,
    P_Value = chi_square$p.value
  ))
}

rownames(chi_square_results) <- Label


chi_square_results %>% 
 kable() %>% 
 kable_styling( bootstrap_options = c("striped", "hover", "condensed")) %>% 
    footnote(general_title = "\n", general = "Table 1")


```


## Numeric Variables
```{r numeric var, fig.height=8, fig.width=11}

numeric_var <- housing %>% 
  select(age, y, previous, unemploy_rate, cons.price.idx, cons.conf.idx, inflation_rate, spent_on_repairs, campaign)


numeric_var %>%
  gather(Variable, value, -y) %>%
    ggplot(aes(y, value, fill=y)) + 
      geom_bar(position = "dodge", stat = "summary", fun = "mean") + 
      facet_wrap(~Variable, scales = "free", ncol = 4, labeller= labeller(Variable = c(
                     `age` = "Age",
                     `previous` = "Contact before Campaign",
                     `unemploy_rate` = "Unemployment Rate",
                     `cons.price.idx` = "Consumer Price Index",
                     `cons.conf.idx` = "Consumer Confidence Index",
                     `campaign` = "Contacts for Campaign",
                     `inflation_rate` = "Inflation Rate",
                     `spent_on_repairs` = "Amount Spent on Repairs"))) +
      scale_fill_manual(values = palette2) +
      labs(x="Credit", y="Value", 
           title = "Feature Associations with the Likelihood of Credit Acceptance",
           subtitle = "Continous features") +
      theme(legend.position = "none") +
    theme(plot.subtitle = element_text(size = 12,face = "italic"),
        plot.title = element_text(size = 18, face = "bold"), 
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
```

```{r numeric var density, fig.height=8, fig.width=13}

numeric_var %>%
    gather(Variable, value, -y) %>%
    ggplot() + 
    geom_density(aes(value, color=y), fill = "transparent") + 
   facet_wrap(~Variable, scales = "free", ncol = 4, labeller= labeller(Variable = c(
                     `age` = "Age",
                     `previous` = "Contact before Campaign",
                     `unemploy_rate` = "Unemployment Rate",
                     `cons.price.idx` = "Consumer Price Index",
                     `cons.conf.idx` = "Consumer Confidence Index",
                     `inflation_rate` = "Inflation Rate",
                     `campaign` = "Contacts for Campaign",
                     `spent_on_repairs` = "Amount Spent on Repairs")))+
  scale_color_manual(values = palette1) +
    labs(title = "Feature Distributions Based on Credit Acceptance",
         subtitle = "Continous features") +
  theme(plot.subtitle = element_text(size = 12,face = "italic"),
        plot.title = element_text(size = 18, face = "bold"), 
        axis.text.x=element_text(size=9),
        axis.text.y=element_text(size=9), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
```




```{r anova test}

anova_var <- c("age", "previous", "unemploy_rate", "cons.price.idx", "cons.conf.idx", "inflation_rate", "spent_on_repairs", "campaign")

new_names <- c("age" = "Age",
                "previous" = "Contact before Campaign",
                "unemploy_rate" = "Unemployment Rate",
                "cons.price.idx" = "Consumer Price Index",
                "cons.conf.idx" = "Consumer Confidence Index",
                "inflation_rate" = "Inflation Rate",
                "spent_on_repairs" = "Amount Spent on Repairs",
               "campaign" = "Contacts for Campaign")

anova_results <- data.frame(
                            Df = integer(), 
                            Sum_Sq = numeric(), 
                            Mean_Sq = numeric(), 
                            F_value = numeric(), 
                            P_Value = numeric(), stringsAsFactors = FALSE)

for (var in anova_var) {
  anova_result <- aov(numeric_var[[var]] ~ numeric_var$y)
  summary_data <- summary(anova_result)[[1]][, c("Df", "Sum Sq", "Mean Sq", "F value", "Pr(>F)")][1:1, ]
  anova_results <- rbind(anova_results, summary_data)
}


rownames(anova_results) <- new_names


anova_results %>% 
 kable() %>% 
 kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>% 
    footnote(general_title = "\n", general = "Table 2")


```

# Logistic Regression

```{r housing model, max.height='200px'}

housingModel <- glm(y_numeric ~ .,
                  data=housingTrain %>% 
                    dplyr::select(age, job, marital, education, taxLien, mortgage, taxbill_in_phl, contact, month, day_of_week, campaign, pdays, poutcome, unemploy_rate, cons.conf.idx, cons.price.idx, inflation_rate, spent_on_repairs, y_numeric), family="binomial" (link="logit"))

housing_sum <- summary(housingModel)
coefficients_table <- as.data.frame(housing_sum$coefficients)

coefficients_table$significance <- ifelse(coefficients_table$`Pr(>|z|)` < 0.001, '***',
                                         ifelse(coefficients_table$`Pr(>|z|)` < 0.01, '**',
                                                ifelse(coefficients_table$`Pr(>|z|)` < 0.05, '*',
                                                       ifelse(coefficients_table$`Pr(>|z|)` < 0.1, '.', ''))))

coefficients_table$p_value <- paste0(round(coefficients_table$`Pr(>|z|)`, digits = 3), coefficients_table$significance)

coefficients_table %>%
  select(-significance, -`Pr(>|z|)`) %>% 
  kable(align = "r") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  footnote(general_title = "\n", general = "Table 3")
```



```{r fitting housing model, warning=FALSE}

set.seed(479)
trainIndex <- createDataPartition(y = paste(housing$taxLien, housing$education) , p = .65,
                                  list = FALSE,
                                  times = 1)
housingTrain <- housing[ trainIndex,]
housingTest  <- housing[-trainIndex,]

housingModel <- glm(y_numeric ~ .,
                  data=housingTrain %>% 
                    dplyr::select(age, job, marital, education, taxLien, mortgage, taxbill_in_phl, contact, month, day_of_week, campaign, pdays, poutcome, unemploy_rate, cons.conf.idx, cons.price.idx, inflation_rate, spent_on_repairs, y_numeric), family="binomial" (link="logit"))


testProbs <- data.frame(Outcome = as.factor(housingTest$y_numeric),
                        Probs = predict(housingModel, housingTest, type= "response"))

testProbs <- 
  testProbs %>%
  mutate(predOutcome  = as.factor(ifelse(testProbs$Probs > 0.5 , 1, 0)))  

 
mosaicplot(confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")$table, color=c("#DBC2CF","#9FA2B2"), main = "Mosaic Plot for Original Confusion Matrix",
           xlab = "Prediction", ylab = "Reference")


housingmatrix <- as.data.frame(as.table(confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")$table))
housingmatrix %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  footnote(general_title = "\n", general = "Table 4")
```

# Improving Model

```{r feature engineering}

housing <- housing %>% 
  mutate(edu = case_when(
    education == "high.school" | education == "professional.course" | education == "university.degree" ~ "highschool.above", 
    TRUE ~ "highschool.below"),
    employment = case_when(
      job == "self-employed" ~ "self-employed", 
      job == "retired" | job == "unemployed" | job == "student" | job == "unknown" | job == "housemaid" ~ "not-employed",
      job == "blue-collar" ~ "blue-collar", 
      TRUE ~ "white-collar"))
  
housing$age_group <- cut(housing$age, breaks = c(0, 30, 50, Inf), labels = c("young_adult", "middle_age", "old_adult"))
housing$job_education_interaction <- paste(housing$edu, housing$employment, sep="_")
housing$campaign_efficiency <- housing$previous / housing$campaign
housing$economic_conditions <- (housing$unemploy_rate + housing$cons.price.idx + housing$cons.conf.idx - housing$inflation_rate) / 4
imbalance_weight <- sum(housing$y_numeric == 0) / sum(housing$y_numeric == 1)

```


```{r improved model, warning=FALSE}

improvedModel <- glm(y_numeric ~ .,
                  data=housingTrain %>% 
                    dplyr::select(y_numeric, age_group, job_education_interaction, mortgage, pdays, taxbill_in_phl, contact, poutcome, economic_conditions, previous, campaign_efficiency),  weights = ifelse(y_numeric == 1, imbalance_weight, 1), 
                  family="binomial" (link="logit"))

improved_sum <- summary(improvedModel)
coefficients_table <- as.data.frame(improved_sum$coefficients)

coefficients_table$significance <- ifelse(coefficients_table$`Pr(>|z|)` < 0.001, '***',
                                         ifelse(coefficients_table$`Pr(>|z|)` < 0.01, '**',
                                                ifelse(coefficients_table$`Pr(>|z|)` < 0.05, '*',
                                                       ifelse(coefficients_table$`Pr(>|z|)` < 0.1, '.', ''))))

coefficients_table$p_value <- paste0(round(coefficients_table$`Pr(>|z|)`, digits = 3), coefficients_table$significance)

coefficients_table %>%
  select(-significance, -`Pr(>|z|)`) %>% 
  kable(align = "r") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  footnote(general_title = "\n", general = "Table 5")
```



```{r fit improved model, warning=FALSE}
set.seed(479)
trainIndex <- createDataPartition(housing$y , p = .65,
                                  list = FALSE,
                                  times = 1)
housingTrain <- housing[ trainIndex,]
housingTest  <- housing[-trainIndex,]

improvedModel <- glm(y_numeric ~ .,
                  data=housingTrain %>% 
                    dplyr::select(y_numeric, age_group, job_education_interaction, mortgage, pdays, taxbill_in_phl, contact, poutcome, economic_conditions, previous, campaign_efficiency),  weights = ifelse(y_numeric == 1, imbalance_weight, 1), 
                  family="binomial" (link="logit"))

testProbs <- data.frame(Outcome = as.factor(housingTest$y_numeric),
                        Probs = predict(improvedModel, housingTest, type= "response"))

testProbs <- 
  testProbs %>%
  mutate(predOutcome  = as.factor(ifelse(testProbs$Probs > 0.5 , 1, 0)))  


mosaicplot(confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")$table, color=c("#DBC2CF","#9FA2B2"), main = "Mosaic Plot for Improved Confusion Matrix",
           xlab = "Prediction", ylab = "Reference")


improvedmatrix <- as.data.frame(as.table(confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")$table))

improvedmatrix %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  footnote(general_title = "\n", general = "Table 6")

```

# Cross Validation

```{r cross validation, warning=FALSE}
ctrl <- trainControl(method = "cv", number = 100, classProbs=TRUE, summaryFunction=twoClassSummary)

cvFit_original <- train(y ~ .,
                  data=housing %>% 
                    dplyr::select(age, job, marital, education, taxLien, mortgage, taxbill_in_phl, contact, month, day_of_week, campaign, pdays, poutcome, unemploy_rate, cons.conf.idx, cons.price.idx, inflation_rate, spent_on_repairs, y), 
                method="glm", family="binomial",
   
                             metric="ROC", trControl = ctrl)
cvFit_improved <- train(y ~ .,
                  data=housing %>% 
                    dplyr::select(y, age_group, job_education_interaction, mortgage, pdays, taxbill_in_phl, contact, poutcome, economic_conditions, previous, campaign_efficiency),   weights = ifelse(y == "Yes", imbalance_weight, 1),
                method="glm", family="binomial",
                metric="ROC", trControl = ctrl)
```


```{r CV plot original, warning=FALSE, message=FALSE}

dplyr::select(cvFit_original$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFit_original$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
    geom_histogram(bins=20, fill = "#DBC2CF") +
    facet_wrap(~metric) +
    geom_vline(aes(xintercept = mean), colour = "#2E4756", linetype = 2, size = 0.6) +
    scale_x_continuous(limits = c(0, 1)) +
    labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics Original Model",
         subtitle = "Across-fold mean reprented as dotted lines") + 
   theme(plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
  
```


```{r CV plot improved, warning=FALSE, message=FALSE}
dplyr::select(cvFit_improved$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFit_improved$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
    geom_histogram(bins=20, fill = "#DBC2CF") +
    facet_wrap(~metric) +
    geom_vline(aes(xintercept = mean), colour = "#2E4756", linetype = 2, size = 0.8) +
    scale_x_continuous(limits = c(0, 1)) +
    labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics for Improved Model",
         subtitle = "Across-fold mean reprented as dotted lines") + 
  theme(plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))

```


```{r auc, warning=FALSE, message=FALSE, include=FALSE}

auc(testProbs$Outcome, testProbs$Probs)

```

```{r auc plot, warning=FALSE}
ggplot(testProbs, aes(d = as.numeric(Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#2E4756") +
    labs(title = "ROC Curve for Improved Model") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = "#DBC2CF") +
  theme(plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
  
```

# Cost Benefit Analysis
True Positive
Marketing resources allocation = $2,850
Credit allocation per homeowner = $5,000
Premium from transacted home = $10,000
Aggregate premium from surrounding homes = $56,000

-2850 * Count - 5000 * Count * 0.25 + 66000 * Count

Total Costs for TP = $2,850 + ($5,000 * 25%) 
Total Benefits for TP = $10,000 (transacted home premium) + $56,000 (aggregate premium) = $66,000

True Negative
No marketing resources allocated = $0
No credit allocated = $0

False Positive
Marketing resources allocation = $2,850

False Negative 
No marketing resources allocated = $0
No credit allocated = $0

```{r cost benefit analysis}

cost_benefit_table <-
   testProbs %>%
      count(predOutcome, Outcome) %>%
      summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>%
       gather(Variable, Count) %>%
       mutate(Revenue =
               ifelse(Variable == "True_Negative", Count * 0,
               ifelse(Variable == "True_Positive", 61900 * Count,
               ifelse(Variable == "False_Negative", 0 * Count,
               ifelse(Variable == "False_Positive", (-2850) * Count, 0)))))
   
kable(cost_benefit_table,
       caption = "Cost Benefit Table") %>% 
kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  footnote(general_title = "\n", general = "Table 7")

```


```{r threshold table}

x = .01
all_threshold <- data.frame()

while (x <= 1) {
threshold<- 
  testProbs %>%
  mutate(predOutcome  = as.factor(ifelse(testProbs$Probs > x , 1, 0))) %>% 
  count(predOutcome, Outcome) %>% 
  summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>% 
  gather(Variable, Count) %>% 
  mutate(threshold = x )

all_threshold <- rbind(all_threshold, threshold)
 x <- x + .01
}


```



```{r threshold plot, message=FALSE, warning=FALSE}

all_threshold %>% 
  ggplot() +
  geom_line(aes(x = threshold, y=Count, color = Variable), size = 1.5, linetype = 1) + 
  scale_color_manual(values = palette4, guide=FALSE) + 
  facet_wrap(~Variable) + 
  labs(title = "Confusion Metric Outcomes for Each Threshold") +
  xlab("Threshold") + 
  theme(plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
  

```



```{r iterative function}

iterateThresholds <- function(data) {
  x = .01
  all_prediction <- data.frame()
  while (x <= 1) {
  
  this_prediction <-
      testProbs %>%
      mutate(predOutcome = ifelse(Probs > x, 1, 0)) %>%
      count(predOutcome, Outcome) %>%
      summarize(True_Negative = sum(n[predOutcome==0 & Outcome==0]),
                True_Positive = sum(n[predOutcome==1 & Outcome==1]),
                False_Negative = sum(n[predOutcome==0 & Outcome==1]),
                False_Positive = sum(n[predOutcome==1 & Outcome==0])) %>%
     gather(Variable, Count) %>%
     mutate(Revenue =
               ifelse(Variable == "True_Negative", Count * 0,
               ifelse(Variable == "True_Positive", 61900 * Count,
               ifelse(Variable == "False_Negative", 0 * Count,
               ifelse(Variable == "False_Positive", (-2850) * Count, 0)))),
            Threshold = x)
  
  all_prediction <- rbind(all_prediction, this_prediction)
  x <- x + .01
  }
return(all_prediction)
}
```



```{r threshold over revenue and, fig.height=6}

whichThreshold <- iterateThresholds(testProbs)

whichThreshold_revenue <- 
whichThreshold %>% 
    group_by(Threshold) %>% 
    summarize(Revenue = sum(Revenue))

plot1 <- ggplot(whichThreshold_revenue)+
  geom_line(aes(x = Threshold, y = Revenue), linewidth = 2, color = "#DBC2CF")+
  geom_vline(xintercept =  pull(arrange(whichThreshold_revenue, -Revenue)[1,1]), color = "#9FA2B2", linewidth = 2.5)+
    labs(title = "Model Revenues By Threshold and Count",
         subtitle = "Vertical Line Denotes Optimal Threshold") + 
  theme(plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))
  
credict_count <-whichThreshold %>% 
  filter(Variable == "True_Positive") %>% 
  mutate(Credit_Count = Count * 0.25)

plot2 <- credict_count %>% 
  ggplot() +
  geom_line(aes(x = Threshold, y = Credit_Count), linewidth = 2, color = "#DBC2CF") + 
  geom_vline(xintercept =  pull(arrange(whichThreshold_revenue, -Revenue)[1,1]), color = "#9FA2B2", linewidth = 2.5) +
   theme(plot.subtitle = element_text(size = 9,face = "italic"),
        plot.title = element_text(size = 12, face = "bold"), 
        axis.text.x=element_text(size=8),
        axis.text.y=element_text(size=8), 
        axis.title=element_text(size=9), 
        panel.background = element_blank(),
        panel.border = element_rect(colour = "grey", fill=NA, linewidth =0.8))

plot1 / plot2 
```


```{r revenue table}

final_table<- data.frame(
  Threshold = c("Optimal_Threshold", "50%_Threshold"),
  Credit = c("34.75", "23.75"),
  Revenue = c("6403900", "4817450")
)

final_table %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  footnote(general_title = "\n", general = "Table 8")
```

